---
title: "TP1"
author: "Jose Daniel"
date: "2022-10-05"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R exercices
## Basic object manipulation and inspection

### 1.Vectors
### 1.1 Let’s start simple

Creation of the following vectors
```{r cars}
e1 <- c(2, 5, 0, 8)
e2 <- (1:200)
e3 <- seq(200, 210, by = 2)
e4 <- c(2, 4, 8, 16, 32, 64, 128)
```

Creation of the vector v of 50 elements such that v[2i] = −1, v[2i + 1] = 1,

Create the vector e5 = (1, 2, ...210) by concatenating e2 and e3.

```{r}
e5 <- c(e2,e3)
```

Create the vector e7 containing 70 equally spaced values between 0 and 1.
```{r}
e7 <- seq(0, 1, length = 70)
```

Create the vector e8 containing 10 times the sequence e1.
```{r}
e8 <- rep(e1, times = 10)
```

What is the result of the operation e2 − e3 ? This is called recycling, and this is dangerous
```{r}
r <- e2 - e3
```
la taille d'un objet plus long n'est pas multiple de la taille d'un objet plus court

### 1.2 Character vectors

Create a vector vowels containing all vowels

```{r}
vowels <- c('a', 'e', 'i', 'o', 'u')
```

letters is a character vector containing all the letters in alphabetical order.
```{r}
letters
```

What does letters %in% vowels do ?
```{r}
letters %in% vowels
```
An array of booelean its true when the letter is the same that the vowel

Extract the number of each vowel
```{r}
which(letters %in% vowels)
```

Extract the number of each non-vowel
```{r}
length(letters) - length(vowels)
```

What are the letters right after a vowel ?
```{r}
letters[which(letters %in% vowels) + 1]
```

Create the string myname containing your name (in lower case)
```{r}
myname <- 'josedaniel'
```

Use strsplit to extract individual letters of your name. Observe that strsplit returns a list. Access its
first element.
```{r}
myname <- 'josedaniel'
lettersofmyname <- strsplit(myname, "")[[1]]
```

Give for each character of your name its number in the alphabet.
```{r}
myname <- 'josedaniel'
lettersofmyname <- strsplit(myname, "")[[1]]
letters[which(letters %in% lettersofmyname)]
which(letters %in% lettersofmyname)
```

Do the same with your right neighbor’s name.
```{r}
myname <- 'josedaniel'
lettersofmyname <- strsplit(myname, "")[[1]]
letters[which(letters %in% lettersofmyname)+1]
which(letters %in% lettersofmyname)+1
```

Who is on average lower in the alphabet ?
```{r}

```

### 2.DataFrames
### 2.1 Cute animals.

Create a dataframe that contains 3 columns: the alphabet letters, the number of each letter, and a binary variable
voyel.
```{r}
number <- which(letters%in%letters)
isvowel <- letters%in%vowels
df1<-data.frame(letters,number, isvowel)
print(df1)
```

Extract the lines of the dataframe corresponding to your name.
```{r}
df1[which(letters %in% lettersofmyname),]
```

Let’s work on the msleep dataset. It contains information about the sleeping patterns of many animals:
```{r}
library(ggplot2)
data(msleep)
msleep
```

Examine the dataset: head, str, names, summary
```{r}
head(msleep)
str(msleep)
names(msleep)
summary(msleep)
```

Sanity check: make sure that animals are either awake either asleep over the course of 24hrs
```{r}
msleep$awake + msleep$sleep_total
```


What is the animal that sleeps the most ?
```{r}
msleep[which.max(msleep$sleep_total),]
```

How many animals of less than 100g and sleep more than half a day ?
```{r}
#msleep[which(msleep$bodywt < 100 & msleep$sleep_total > 12),]
length(which(msleep$bodywt < 100 & msleep$sleep_total > 12))
```

What is the average brain weight/body weigth ratio ?
```{r}
mean(msleep$brainwt[which(is.na(msleep$brainwt) == FALSE)] / msleep$bodywt[which(is.na(msleep$brainwt) == FALSE)])
```

Who has the highest such ratio ?
```{r}
msleep[which.max(msleep$brainwt[which(is.na(msleep$brainwt) == FALSE)] / msleep$bodywt[which(is.na(msleep$brainwt) == FALSE)]),]
```

### 2.2 Endangered animals: let us consider the case of Threatened or extinct animals
create a copy of msleep and reorder its factors according to the presented order. To create an ordered factor,
use the ordered=TRUE option of the factor function
```{r}
copymsleep = msleep
copymsleep$conservation = factor(copymsleep$conservation, levels = c("lc", "domesticated", "cd", "nt", "vu", "en"), ordered = TRUE)
subset(copymsleep, conservation >= "en")
 
```

use the ordered factors to compare the average weight to isolate threatened animals and compute their average
weight
```{r}

mean(copymsleep$bodywt[f == "cd" | f == "vu" | f == "en"])
```

compare this weight to the weight of the remaining animals
```{r}
mean(copymsleep$bodywt[f != "cd" | f != "vu" | f != "en"])
```

add a boolean column to the dataframe, threatened, that is true if the animal is threatened
```{r}
threatened_animals <- copymsleep[which(copymsleep$conservation == "en" | copymsleep$conservation == "vu" | copymsleep$conservation == "cd"),]
copymsleep$conservation %in% threatened_animals$conservation
copymsleep$threatened <- copymsleep$conservation %in% threatened_animals$conservation
```


### 2.3 Functions

• Create a function returning taking a name as input, and returning the corresponding letter numbers.
```{r}
letter_numbers <- function(name) {
  if(is.na(name) || name == ""){
    return ("Give a correct name")
  }
  lettersofname <- strsplit(name, "")[[1]]
  return (which(letters %in% lettersofname))
}
letter_numbers("josedaniel")
```

• What happends if you give an empty ”” name to this function ? Fix accordingly.
```{r}
letter_numbers("")
```

• What happends if you give to this function non-standard characters ? Fix the problem. Tip: choose one strategy:
regexp, NA, substr and tolower
```{r}
letter_numbers("jose?kbi€")
```

• Create a function that take an animal name as input, and returns its genus under the form ”The Goat is a Capri”
if it is in the msleep dataset, and ”I don’t know” otherwise.
```{r}
is_in_msleep <- function(name){
  indx <- which(msleep$name == name)
  r <- "hi"
  if(indx>0) {
    s1 <- "The"
    s2 <- "is a"
    r <- paste(s1,name,s2,msleep$genus[indx],sep =" ")
  }else{
    r <- "I don't know."
  }
  return (r)
  #browser()
}

```

• The browser() command allows debugging. When R encounters this call, it stops the execution of a function
and provides the user with a different Browse prompt. Place a browser somewhere in your function, and
run this function. Print some local variables. You can continue the execution with n, and quit the browser mode
with Q.
```{r}

```

