---
title: "tp2"
author: "Jose Daniel"
date: "2022-10-10"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Plots and more complex procedures

## 1 Plots and Given Names

Read the table prenoms.csv and inspect it

```{r}
prenoms <- read.csv("/home/organist/Documents/exploratory_analysis_dataviz/prenoms.csv",sep=";")

library(tidyverse)
library(ggrepel)

head(prenoms)

```

### Plots

The number of births by year

```{r}
prenoms  %>% group_by(Année) %>% summarise(tot=sum(Nombre)) ->stata

stata %>% ggplot(aes(x=Année,y=tot))+geom_line()
```
The number of male/female births by yea
```{r}
prenoms  %>% group_by(Année,Sexe) %>% summarise(tot=sum(Nombre)) ->stata2

stata2 %>% ggplot(aes(x=Année,y=tot, group=Sexe, color=Sexe))+geom_line()
```
Is your name in the dataset ?
```{r}
tocayos <- prenoms[which(prenoms$Prénom == "Daniel"),]
tocayos
```

Represent the 10 most given names

```{r}
prenoms  %>% group_by(Prénom) %>% summarise(tot=sum(Nombre)) -> top10names
top10names <- top10names[order(- top10names$tot),]
head(top10names,10)
```
Select for each year the top 5 given names by sex and represent their evolution along years.

```{r}
require("ggrepel")
prenoms %>% group_by(Année,Prénom) %>% summarise(tot=sum(Nombre)) %>% slice_max(order_by = tot, n = 5) -> topNames
top5_by_year = prenoms %>% group_by(Année,Sexe) %>% arrange(desc(Nombre)) %>% slice(1:5)
top5_by_year %>% ggplot(aes(x=Année,y=Nombre, group=Sexe, color=Sexe))+geom_point()+geom_label_repel(aes(label=Prénom),size = 3)

```

- Plot the average number of letters by year
```{r}
prenoms_nb_letter <- prenoms
prenoms_nb_letter$NB_Letters <- nchar(prenoms$Prénom)
prenoms_nb_letter$total_Letters_by_prenom <- nchar(prenoms$Prénom) * prenoms$Nombre
mean_letters_by_year <- prenoms_nb_letter %>% group_by(Année) %>% summarise(mean_letters_by_year=sum(total_Letters_by_prenom)/sum(Nombre))
mean_letters_by_year %>% ggplot(aes(x=Année,y=tot))+geom_point()

```

- Plot the average number of vowels/consonants by year
```{r}
prenoms_vowels_consonants <- prenoms
prenoms_vowels_consonants$vowels <- nchar(gsub("[^aeiouy]","",prenoms$Prénom, ignore.case = TRUE))
prenoms_vowels_consonants$consonants <- nchar(prenoms$Prénom) - nchar(gsub("[^aeiouy]","",prenoms$Prénom, ignore.case = TRUE))
prenoms_vowels_consonants$total_vowels <- prenoms_vowels_consonants$Nombre * prenoms_vowels_consonants$vowels
prenoms_vowels_consonants$total_consonants <- prenoms_vowels_consonants$Nombre * prenoms_vowels_consonants$consonants
mean_vowels_consonants_by_year <- prenoms_vowels_consonants %>% group_by(Année) %>% summarise(mean_vowels_by_year=sum(total_vowels)/sum(Nombre), mean_consonants_by_year=sum(total_consonants)/sum(Nombre))
mean_vowels_consonants_by_year
```

- How the number of composed names (like Jean-Baptiste or Lou-Ann)
```{r}
composed_names <- prenoms[which(grepl("-",prenoms$Prénom)),]
head(composed_names)
```

- Define a “hype” criteria and find the hypest names
```{r}
hype_names = prenoms[which(grepl("é",prenoms$Prénom) & grepl("y",prenoms$Prénom)),]
hype_names %>% group_by(Prénom) %>% summarise(tot=sum(Nombre)) -> stata
stata
```

## Exploring the Gray city

• read the table prenomsParis.csv

```{r}
prenoms_paris <- read.csv("/home/organist/Documents/exploratory_analysis_dataviz/prenomsParis.csv",sep=";")

library(tidyverse)
library(ggrepel)

head(prenoms_paris)
```


• repeat what you’ve done with Toulouse, rewriting as little as possible

```{r}
prenoms_paris  %>% group_by(Annee) %>% summarise(tot=sum(Nombre)) ->stata

stata %>% ggplot(aes(x=Annee,y=tot))+geom_line() + ggtitle("Number of births by year")
```
```{r}
prenoms_paris  %>% group_by(Annee,Sexe) %>% summarise(tot=sum(Nombre)) ->stata2

stata2 %>% ggplot(aes(x=Annee,y=tot, group=Sexe, color=Sexe))+geom_line() + ggtitle("Number of male/female/X births by year")
```

```{r}
prenoms_paris  %>% group_by(Prenoms) %>% summarise(tot=sum(Nombre)) -> top10names_paris
top10names_paris <- top10names_paris[order(- top10names_paris$tot),]
head(top10names_paris,10)
```
```{r}
top5_by_year_paris = prenoms_paris %>% group_by(Annee,Sexe) %>% arrange(desc(Nombre)) %>% slice(1:5)
top5_by_year_paris %>% ggplot(aes(x=Annee,y=Nombre, group=Sexe, color=Sexe))+geom_point()+geom_label_repel(aes(label=Prenoms),size = 3) + ggtitle("top 5 given names by sex, Evolution along years.")
```
Plot the average number of letters by year (A complete)
```{r}
prenoms_nb_letter <- prenoms
prenoms_nb_letter$NB_Letters <- nchar(prenoms$Prénom)
prenoms_nb_letter$total_Letters_by_prenom <- nchar(prenoms$Prénom) * prenoms$Nombre
mean_letters_by_year <- prenoms_nb_letter %>% group_by(Année) %>% summarise(mean_letters_by_year=sum(total_Letters_by_prenom)/sum(Nombre))
mean_letters_by_year %>% ggplot(aes(x=Année,y=tot))+geom_point()
```

A tale of two cities
• Combine observations made on the two cities.
• Normalise by the number of births.

```{r}
prenoms  %>% group_by(Année) %>% summarise(tot=sum(Nombre)) ->stata
prenoms$Nombre_Norm = prenoms$Nombre / stata$tot[which(stata$Année == prenoms$Année)]
stata
```


• What are the most unshared names ?
A tale of many cities
• Read the table prenomsRennesStrassNantesToul.csv
• Inspect it. On the opendata website the description is the following: