---
title: "Football_Player_Stats"
author: "Jose Daniel"
date: "2022-11-16"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Football Player Stats

This notebook is the exploratory data analysis of 2021-2022 Football Player Stats. Taken the dataset from kaggle https://www.kaggle.com/datasets/vivovinco/20212022-football-player-stats. This dataset contains 2021-2022 football player stats per 90 minutes. Only players of Premier League, Ligue 1, Bundesliga, Serie A and La Liga are listed.

The first thing we noticed about the data is that they were measured by 90 minutes played. So we transformed them into statistics for the whole session.


```{r cars}
players <- read.csv("./2021-2022_Football_Player_Stats.csv",sep=";")

players['Player'] = players['Player']
players['Nation'] = players['Nation']
players['Pos'] = players['Pos']
players['Squad'] = players['Squad']
players['Comp'] = players['Comp']
players['Age'] = players['Age']
players['MP'] = players['MP']
players['G.90'] = players['Goals']
players['G.Sh'] = players['G.Sh']
players['PKGoals'] = round(((players['ShoPK'] * players['Min']) / 90),0)
players['PKAttempted'] = round(((players['PKatt'] * players['Min']) / 90),0)
players['Goals_tot'] = round(((players['G.90'] * players['Min']) / 90),0)
players['Pass'] = round(((players['PasTotAtt'] * players['Min']) / 90),0)
players['PassCompleted'] = round(((players['PasTotCmp'] * players['Min']) / 90),0)
players['PassComp%'] = round(((players['PassCompleted'] / players['Pass']) * 100),2)
players['Assist'] = round(((players['Assists'] * players['Min']) / 90),0)
players['Cross'] = round(((players['PasCrs'] * players['Min']) / 90),0)
players['CrossCompleted'] = round(((players['CrsPA'] * players['Min']) / 90),0)
players['CrossComp%'] = round(((players['CrossCompleted'] / players['Cross']) * 100),2)
players['Tackle_Won'] = round(((players['TklWon'] * players['Min']) / 90),0)
players['SucDribble'] = round(((players['DriSucc'] * players['Min']) / 90),0)
players['Dribble'] = round(((players['DriAtt'] * players['Min']) / 90),0)
players['DribbleComp%'] = round(((players['SucDribble'] / players['Dribble']) * 100),2)
players['YCards'] = round(((players['CrdY'] * players['Min']) / 90),0)
players['RCards'] = round(((players['CrdR'] * players['Min']) / 90),0)
players['Fls'] = round(((players['Fls'] * players['Min']) / 90),0)
players['Fld'] = round(((players['Fld'] * players['Min']) / 90),0)
players['OGoals'] = round(((players['OG'] * players['Min']) / 90),0)
players['AerWon'] = round(((players['AerWon'] * players['Min']) / 90),0)
players['AerLost'] = round(((players['AerLost'] * players['Min']) / 90),0)
players['AerWon%'] = round(((players['AerWon'] / (players['AerWon'] + players['AerLost'])) * 100),2)
players['TouAtt3rd'] = round(((players['TouAtt3rd'] * players['Min']) / 90),0)

head(players)
```

## Libraries

The libraries we used to make the different plots to install them we use CRAN. The explication of each one is on the Readme

```{r pressure, echo=FALSE}
library(tidyverse)
library(ggrepel)
library(hrbrthemes)
library(Hmisc)
library(GGally)
library(corrplot)
library(viridis)
library(gridExtra)
library(car)
library(cowplot)
library(fmsb)
library(ggradar)
library(plotly)
```
We have seen some basic facts about this dataset like the player that make the most numbers of goals

```{r}
players[which.max(players$Goals_tot),]
```
we can use this variable to classify the dataset and see the players who scored the most goals in the season.
```{r}
by_goals <- players[order(-players$Goals_tot),] 
head(by_goals)

```

To make a deeper analysis we have seen the different position by player.
```{r}

position = unique(players$Pos)
position

```
We keep the 4 most recognized positions in soccer such as attackers, defenders, midfielders and goalkeepers.
```{r}
goal_keepers = players[which(players$Pos == "GK"),]
defenders = players[which(players$Pos == "DF" | players$Pos == "DFMF" | players$Pos == "DFFW"),]
midfielders = players[which(players$Pos == "MF" | players$Pos == "MFFW" | players$Pos == "MFDF"),]
forwards = players[which(players$Pos == "FW" | players$Pos == "FWMF" | players$Pos == "FWDF"),]
bizard = players[which(players$Pos == "GKMF"),]
```

We can then make an analysis for each type of player by position, such as the defenders who spend more time in the attacking area.

```{r}
defenders <-defenders[order(-defenders$TouAtt3rd),]
head(defenders)
```
Now the question is how to recognize a good player. Let's compare a variable such as total goals by each type of player.

```{r}

describe(defenders$Goals_tot)
describe(midfielders$Goals_tot)
describe(goal_keepers$Goals_tot)
describe(forwards$Goals_tot)
```
But this variable is not enough to know if he is a good player so we add more variables to the observation and through a boxplot we can appreciate the capabilities where according to the type of player each player stands out.

SoT%: Shots on target percentage
PasTotCmp%: Pass completion percentage
TklDri%: Percentage of dribblers tackled
Press%: Percentage of time the squad gained possession withing five seconds of applying pressure
DriSucc%: Percentage of dribbles completed successfully
Rec%: Percentage of time a player successfully received a pass
AerWon: Percentage of aerials won

```{r}

data <- players %>% select(Pos, Goals_tot, PresSucc, GCA, Blocks, Err, Recov, SoT., PasTotCmp., TklDri., Press., DriSucc., Rec., `AerWon%`)  

data$Pos[players$Pos == "DF" | players$Pos == "DFMF" | players$Pos == "DFFW"] <- "DF"
data$Pos[players$Pos == "MF" | players$Pos == "MFFW" | players$Pos == "MFDF"] <- "MF"
data$Pos[players$Pos == "FW" | players$Pos == "FWMF" | players$Pos == "FWDF"] <- "FW"
data$Pos[players$Pos == "GK" | players$Pos == "GKMF" ] <- "GK"

data
bp1 <- ggplot(data,  aes(x=Pos, y=Goals_tot, fill=Pos)) + geom_boxplot() + ggtitle("Goals_tot by tipe of player")
bp2 <- ggplot(data,  aes(x=Pos, y=PresSucc, fill=Pos)) + geom_boxplot() + ggtitle("PresSucc by tipe of player")
bp3 <- ggplot(data,  aes(x=Pos, y=GCA, fill=Pos)) + geom_boxplot() + ggtitle("GCA by tipe of player")
bp4 <- ggplot(data,  aes(x=Pos, y=Blocks, fill=Pos)) + geom_boxplot() + ggtitle("Blocks by tipe of player")
bp5 <- ggplot(data,  aes(x=Pos, y=Err, fill=Pos)) + geom_boxplot() + ggtitle("Err by tipe of player")
bp6 <- ggplot(data,  aes(x=Pos, y=Recov, fill=Pos)) + geom_boxplot() + ggtitle("Recov by tipe of player")

bp7 <- ggplot(data,  aes(x=Pos, y=SoT., fill=Pos)) + geom_boxplot() + ggtitle("SoT. by tipe of player")
bp8 <- ggplot(data,  aes(x=Pos, y=PasTotCmp., fill=Pos)) + geom_boxplot() + ggtitle("PasTotCmp. by tipe of player")
bp9 <- ggplot(data,  aes(x=Pos, y=TklDri., fill=Pos)) + geom_boxplot() + ggtitle("TklDri. by tipe of player")
bp10 <- ggplot(data,  aes(x=Pos, y=Press., fill=Pos)) + geom_boxplot() + ggtitle("Press. by tipe of player")
bp11 <- ggplot(data,  aes(x=Pos, y=DriSucc., fill=Pos)) + geom_boxplot() + ggtitle("DriSucc. by tipe of player")
bp12 <- ggplot(data,  aes(x=Pos, y=Rec., fill=Pos)) + geom_boxplot() + ggtitle("Rec. by tipe of player")
bp13 <- ggplot(data,  aes(x=Pos, y=`AerWon%`, fill=Pos)) + geom_boxplot() + ggtitle("AerWon by tipe of player")


bp1
bp7
bp8
bp9
bp10
bp11
bp12
bp13
```
In these graphs above, we can see that depending on the type of player some characteristics stand out such as goals for forwards or tackles for defenders.



At this point we wonder if there is any relationship between the country and the types of players. 

```{r}
nationalites = unique(players$Nation)
length(nationalites)
```
As there are quite a few nationalities, we have chosen the 10 most frequent ones in the data set and count each type of player by nationalite.

```{r}
posNation <- players %>% select(Pos, Nation)

posNation$Pos[players$Pos == "DF" | players$Pos == "DFMF" | players$Pos == "DFFW"] <- "DF"
posNation$Pos[players$Pos == "MF" | players$Pos == "MFFW" | players$Pos == "MFDF"] <- "MF"
posNation$Pos[players$Pos == "FW" | players$Pos == "FWMF" | players$Pos == "FWDF"] <- "FW"
posNation$Pos[players$Pos == "GK" | players$Pos == "GKMF" ] <- "GK"

nationFrequency <- posNation %>% group_by(Nation) %>% summarise(total_count=n())
nationFrequency <- nationFrequency[order(-nationFrequency$total_count),] 
topTenNation <- filter(posNation,Nation %in% nationFrequency$Nation[1:10])

posByNation <- topTenNation %>% group_by(Pos,Nation) %>% summarise(total_count=n())
posByNation <- posByNation[order(-posByNation$total_count),]

ggplot(posByNation, aes(fill=Pos, y=total_count, x=Nation)) + geom_bar(position="fill", stat="identity")+ ggtitle("Type of Position by Nation")
```
Is there any relation between the nationality and the statistics of each player? We performed different boxplots with the density called violin to identify this relationship.

```{r}

data <- forwards %>% select(Nation, Goals_tot, PresSucc, GCA, Blocks, Err, Recov, SoT, PasTotCmp, TklDri,Press, DriSucc, Rec, AerWon)  

data_ <- data %>% group_by(Nation) %>% summarise(total_count=n())
data_ <- data_[order(-data_$total_count),] 
my_second_df <- filter(data,Nation %in% data_$Nation[1:10])
vp1 <- ggplot(my_second_df,  aes(x=Nation, y=Goals_tot, fill=Nation)) + geom_violin(width=1.4) + geom_boxplot(width=0.1, color="grey", alpha=0.2)
vp2 <- ggplot(my_second_df,  aes(x=Nation, y=PresSucc, fill=Nation)) + geom_violin(width=1.4) + geom_boxplot(width=0.1, color="grey", alpha=0.2)
vp3 <- ggplot(my_second_df,  aes(x=Nation, y=GCA, fill=Nation)) + geom_violin(width=1.4) + geom_boxplot(width=0.1, color="grey", alpha=0.2)
vp4 <- ggplot(my_second_df,  aes(x=Nation, y=Blocks, fill=Nation)) + geom_violin(width=1.4) + geom_boxplot(width=0.1, color="grey", alpha=0.2)
vp5 <- ggplot(my_second_df,  aes(x=Nation, y=Err, fill=Nation)) + geom_violin(width=1.4) + geom_boxplot(width=0.1, color="grey", alpha=0.2)


vp7 <- ggplot(my_second_df,  aes(x=Nation, y=SoT, fill=Nation)) + geom_violin(width=1.4) + geom_boxplot(width=0.1, color="grey", alpha=0.2)
vp8 <- ggplot(my_second_df,  aes(x=Nation, y=PasTotCmp, fill=Nation)) + geom_violin(width=1.4) + geom_boxplot(width=0.1, color="grey", alpha=0.2)
vp9 <- ggplot(my_second_df,  aes(x=Nation, y=TklDri, fill=Nation)) + geom_violin(width=1.4) + geom_boxplot(width=0.1, color="grey", alpha=0.2)
vp10 <- ggplot(my_second_df,  aes(x=Nation, y=Press, fill=Nation)) + geom_violin(width=1.4) + geom_boxplot(width=0.1, color="grey", alpha=0.2)
vp11 <- ggplot(my_second_df,  aes(x=Nation, y=DriSucc, fill=Nation)) + geom_violin(width=1.4) + geom_boxplot(width=0.1, color="grey", alpha=0.2)
vp12 <- ggplot(my_second_df,  aes(x=Nation, y=Rec, fill=Nation)) + geom_violin(width=1.4) + geom_boxplot(width=0.1, color="grey", alpha=0.2)
vp13 <- ggplot(my_second_df,  aes(x=Nation, y=`AerWon`, fill=Nation)) + geom_violin(width=1.4) + geom_boxplot(width=0.1, color="grey", alpha=0.2)

vp1
vp2
vp3
vp4
vp5
vp7
vp8
vp9
vp10
vp11
vp12
vp13

```
Is there any correlation between a player's and the different stats?

```{r}

allPlayersCorr <- players %>% select(Goals_tot, PresSucc, GCA, Blocks, Err, Recov, SoT, PasTotCmp, TklDri,Press, DriSucc, Rec, DriAtt, RecTarg, TouAttPen,CPA)
forwardsCorr <- forwards %>% select(Goals_tot, PresSucc, GCA, Blocks, Err, Recov, SoT, PasTotCmp, TklDri,Press, DriSucc, Rec, DriAtt, RecTarg, TouAttPen,CPA)
defendersCorr <- defenders %>% select(Goals_tot, PresSucc, GCA, Blocks, Err, Recov, SoT, PasTotCmp, TklDri,Press, DriSucc, Rec, DriAtt, RecTarg, TouAttPen,CPA)
midfieldersCorr <- midfielders %>% select(Goals_tot, PresSucc, GCA, Blocks, Err, Recov, SoT, PasTotCmp, TklDri,Press, DriSucc, Rec, DriAtt, RecTarg, TouAttPen,CPA)
goalKeepersCorr <- goal_keepers %>% select(Goals_tot, PresSucc, GCA, Blocks, Err, Recov, SoT, PasTotCmp, TklDri,Press, DriSucc, Rec, DriAtt, RecTarg, TouAttPen,CPA)

ggcorr(allPlayersCorr, method = c("everything", "pearson")) + ggtitle("All players")


ggcorr(forwardsCorr, method = c("everything", "pearson")) + ggtitle("Forwards")
ggcorr(defendersCorr, method = c("everything", "pearson")) + ggtitle("Defender")
ggcorr(midfieldersCorr, method = c("everything", "pearson")) + ggtitle("Midfielders")
ggcorr(goalKeepersCorr, method = c("everything", "pearson")) + ggtitle("Goalkeeper")

```

Is there a relationship between age and player performance?

```{r}

defendersByAge <- defenders %>% select(Age, Tkl) %>% group_by(Age) %>% summarise(total_count=mean(Tkl))
defendersByAge <- filter(defendersByAge,defendersByAge$total_count > 0)

forwardsByAge <- forwards %>% select(Age, Goals_tot) %>% group_by(Age) %>% summarise(total_count=mean(Goals_tot))
forwardsByAge <- filter(forwardsByAge,forwardsByAge$total_count > 0)

midfieldersByAge <- midfielders %>% select(Age, PasAss) %>% group_by(Age) %>% summarise(total_count=mean(PasAss))
midfieldersByAge <- filter(midfieldersByAge,midfieldersByAge$total_count > 0)

goalKeepersByAge <- goal_keepers %>% select(Age, Clr) %>% group_by(Age) %>% summarise(total_count=mean(Clr))
goalKeepersByAge <- filter(goalKeepersByAge,goalKeepersByAge$total_count > 0)

p1 <- plot(defendersByAge$Age, defendersByAge$total_count, lwd=3, col=rgb(0.1,0.7,0.1,0.8), xlab="Age", ylab = "Tkl", main = "Tkl by Age") + lines(lowess(defendersByAge$Age,defendersByAge$total_count))

p2 <- plot(forwardsByAge$Age, forwardsByAge$total_count, lwd=3, col=rgb(0.1,0.7,0.1,0.8), xlab="Age", ylab = "Goals", main = "Goals by Age") + lines(lowess(forwardsByAge$Age,forwardsByAge$total_count))

p3 <- plot(midfieldersByAge$Age, midfieldersByAge$total_count, lwd=3, col=rgb(0.1,0.7,0.1,0.8), xlab="Age", ylab = "PasAss", main = "PasAss by Age") + lines(lowess(midfieldersByAge$Age,midfieldersByAge$total_count))

p4 <- plot(goalKeepersByAge$Age, goalKeepersByAge$total_count, lwd=3, col=rgb(0.1,0.7,0.1,0.8), xlab="Age", ylab = "Clr", main = "Clr by Age") + lines(lowess(goalKeepersByAge$Age,goalKeepersByAge$total_count))

```
Finnaly we see 3 top players to analyze their differences

```{r}
library(ggradar)
players$Player <- sub("<e9>*", "e", players$Player)
bestPlayers <- players %>% select(Player, Goals_tot, Assist, Dribble, Recov, Fls, Fld)

min_max_norm <- function(x) {
 (x - min(x)) / (max(x) - min(x))
}

bestPlayersNorm <- bestPlayers
bestPlayersNorm[2:7] <- as.data.frame(lapply(bestPlayers[2:7], min_max_norm))

bestPlayersNames <- c('Lionel Messi', 'Sadio Mane', 'Kylian Mbappe')
bestPlayers <- filter(bestPlayersNorm,players$Player %in% bestPlayersNames & players$Goals_tot != 0)
bestPlayers

ggradar(bestPlayers)
```

