---
title: "Football_Player_Stats"
author: "Jose Daniel"
date: "2022-11-16"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Football Player Stats

This is an

```{r cars}
players <- read.csv("./2021-2022_Football_Player_Stats.csv",sep=";")

players['Player'] = players['Player']
players['Nation'] = players['Nation']
players['Pos'] = players['Pos']
players['Squad'] = players['Squad']
players['Comp'] = players['Comp']
players['Age'] = players['Age']
players['MP'] = players['MP']
players['G.90'] = players['Goals']
players['G.Sh'] = players['G.Sh']
players['PKGoals'] = round(((players['ShoPK'] * players['Min']) / 90),0)
players['PKAttempted'] = round(((players['PKatt'] * players['Min']) / 90),0)
players['Goals_tot'] = round(((players['G.90'] * players['Min']) / 90),0)
players['Pass'] = round(((players['PasTotAtt'] * players['Min']) / 90),0)
players['PassCompleted'] = round(((players['PasTotCmp'] * players['Min']) / 90),0)
players['PassComp%'] = round(((players['PassCompleted'] / players['Pass']) * 100),2)
players['Assist'] = round(((players['Assists'] * players['Min']) / 90),0)
players['Cross'] = round(((players['PasCrs'] * players['Min']) / 90),0)
players['CrossCompleted'] = round(((players['CrsPA'] * players['Min']) / 90),0)
players['CrossComp%'] = round(((players['CrossCompleted'] / players['Cross']) * 100),2)
players['Tackle_Won'] = round(((players['TklWon'] * players['Min']) / 90),0)
players['SucDribble'] = round(((players['DriSucc'] * players['Min']) / 90),0)
players['Dribble'] = round(((players['DriAtt'] * players['Min']) / 90),0)
players['DribbleComp%'] = round(((players['SucDribble'] / players['Dribble']) * 100),2)
players['YCards'] = round(((players['CrdY'] * players['Min']) / 90),0)
players['RCards'] = round(((players['CrdR'] * players['Min']) / 90),0)
players['Fls'] = round(((players['Fls'] * players['Min']) / 90),0)
players['Fld'] = round(((players['Fld'] * players['Min']) / 90),0)
players['OGoals'] = round(((players['OG'] * players['Min']) / 90),0)
players['AerWon'] = round(((players['AerWon'] * players['Min']) / 90),0)
players['AerLost'] = round(((players['AerLost'] * players['Min']) / 90),0)
players['AerWon%'] = round(((players['AerWon'] / (players['AerWon'] + players['AerLost'])) * 100),2)
players['TouAtt3rd'] = round(((players['TouAtt3rd'] * players['Min']) / 90),0)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
library(tidyverse)
library(ggrepel)

require("ggrepel")
head(players)
```

max goleador

```{r}
players[which.max(players$Goals_tot),]
```
sort by goals
```{r}
by_goals <- players[order(-players$Goals_tot),] 
by_goals

```

defenser with touches in attacking 1/3
```{r}

position = unique(players$Pos)
position
goal_keepers = players[which(players$Pos == "GK"),]
defenders = players[which(players$Pos == "DF" | players$Pos == "DFMF" | players$Pos == "DFFW"),]
midfielders = players[which(players$Pos == "MF" | players$Pos == "MFFW" | players$Pos == "MFDF"),]
forwards = players[which(players$Pos == "FW" | players$Pos == "FWMF" | players$Pos == "FWDF"),]
bizard = players[which(players$Pos == "GKMF"),]
```


```{r}
defenders <-defenders[order(-defenders$TouAtt3rd),]
defenders
```
The best 4 Qualities for playing a particular position 

```{r}
library(hrbrthemes)
max(defenders$Press)
defenders %>% ggplot(aes(x=defenders$Rk,y=defenders$Goals_tot))+geom_point()
goal_keepers %>% ggplot(aes(x=goal_keepers$Rk,y=goal_keepers$Goals_tot))+geom_point()
midfielders %>% ggplot(aes(x=midfielders$Rk,y=midfielders$Goals_tot))+geom_point()
forwards %>% ggplot(aes(x=forwards$Rk,y=forwards$Goals_tot))+geom_point()

players  %>% group_by(Pos) %>% summarise(tot=mean(Goals_tot)) ->stata2
stata2 %>% ggplot(aes(x=Pos,y=tot, group=Pos, color=Pos))+geom_line()+ ggtitle("Number of goals by Pos")

forwards  %>% group_by(Goals_tot) %>% summarise(Freq=n()) ->stata2
stata2 %>% ggplot(aes(x=stata2$Freq,y=stata2$Goals_tot))+geom_point()
p <- stata2 %>%
  ggplot( aes(x=stata2$Goals_tot, y=stata2$Freq)) +
    geom_histogram() +
    ggtitle("Bin size = 3") +
    theme_ipsum() +
    theme(
      plot.title = element_text(size=15)
    )
p
stata2 %>% ggplot(aes(x=Goals_tot,y=Freq, group=Goals_tot, color=Freq))+geom_histogram()+ ggtitle("Number of goals by Pos")

```
```{r}
defenders  %>% group_by(Goals_tot) %>% summarise(Freq=n()) -> defenders_by_Goals
ggplot(mtcars, aes(x=as.factor(Goals_tot), fill=as.factor(Goals_tot) )) + 
  geom_bar( ) +
  scale_fill_hue(c = 40) +
  theme(legend.position="none")
defenders_by_Goals %>% ggplot(aes(x=as.factor(Freq),y=Goals_tot))+geom_bar()+scale_fill_manual(values = Goals_tot )
```


```{r}
library(Hmisc)
describe(defenders$Goals_tot)
describe(midfielders$Goals_tot)
describe(goal_keepers$Goals_tot)
describe(forwards$Goals_tot)
```

```{r}
library(GGally)
library(corrplot)
defenders_ <- defenders %>% select(PresSucc, Press, Blocks, Err, Recov)  
defenders_
forwards_ <- forwards %>% select(Goals_tot, Assists)  
forwards_
cor(forwards_)
ggpairs(defenders_, title="correlogram with ggpairs()")
pairs(defenders_)
```

```{r}
library(tidyverse)
library(hrbrthemes)
library(viridis)
data <- players %>% select(Pos, Goals_tot, PresSucc, GCA, Blocks, Err, Recov)  
data$Pos[players$Pos == "DF" | players$Pos == "DFMF" | players$Pos == "DFFW"] <- "DF"
data$Pos[players$Pos == "MF" | players$Pos == "MFFW" | players$Pos == "MFDF"] <- "MF"
data$Pos[players$Pos == "FW" | players$Pos == "FWMF" | players$Pos == "FWDF"] <- "FW"
data$Pos[players$Pos == "GK" | players$Pos == "GKMF" ] <- "GK"
data
```

```{r}
# Boxplot by category 
bp1 <- ggplot(data,  aes(x=Pos, y=Goals_tot, fill=Pos)) + geom_boxplot()
bp2 <- ggplot(data,  aes(x=Pos, y=PresSucc, fill=Pos)) + geom_boxplot()
bp3 <- ggplot(data,  aes(x=Pos, y=GCA, fill=Pos)) + geom_boxplot()
bp4 <- ggplot(data,  aes(x=Pos, y=Blocks, fill=Pos)) + geom_boxplot()
bp5 <- ggplot(data,  aes(x=Pos, y=Err, fill=Pos)) + geom_boxplot()
bp6 <- ggplot(data,  aes(x=Pos, y=Recov, fill=Pos)) + geom_boxplot()

```

```{r}
library(gridExtra)
grid.arrange(bp1, bp2, bp3, bp4, bp5, bp6, ncol=2, nrow =3)

```

```{r}

bp1 <- ggplot(data,  aes(x=Nation, y=Goals_tot, fill=Nation)) + geom_violin(width=1.4) + geom_boxplot(width=0.1, color="grey", alpha=0.2)
```


```{r}
bp3
```
On va definir certains capacites pour chaque type de jouer

SoT%: Shots on target percentage
PasTotCmp%: Pass completion percentage
TklDri%: Percentage of dribblers tackled
Press%: Percentage of time the squad gained possession withing five seconds of applying pressure
DriSucc%: Percentage of dribbles completed successfully
Rec%: Percentage of time a player successfully received a pass
AerWon: Percentage of aerials won

```{r}
data <- players %>% select(Pos, Goals_tot, PresSucc, GCA, Blocks, Err, Recov, SoT., PasTotCmp., TklDri.,Press., DriSucc., Rec., `AerWon%`)  

data$Pos[players$Pos == "DF" | players$Pos == "DFMF" | players$Pos == "DFFW"] <- "DF"
data$Pos[players$Pos == "MF" | players$Pos == "MFFW" | players$Pos == "MFDF"] <- "MF"
data$Pos[players$Pos == "FW" | players$Pos == "FWMF" | players$Pos == "FWDF"] <- "FW"
data$Pos[players$Pos == "GK" | players$Pos == "GKMF" ] <- "GK"

data
bp1 <- ggplot(data,  aes(x=Pos, y=Goals_tot, fill=Pos)) + geom_boxplot()
bp2 <- ggplot(data,  aes(x=Pos, y=PresSucc, fill=Pos)) + geom_boxplot()
bp3 <- ggplot(data,  aes(x=Pos, y=GCA, fill=Pos)) + geom_boxplot()
bp4 <- ggplot(data,  aes(x=Pos, y=Blocks, fill=Pos)) + geom_boxplot()
bp5 <- ggplot(data,  aes(x=Pos, y=Err, fill=Pos)) + geom_boxplot()
bp6 <- ggplot(data,  aes(x=Pos, y=Recov, fill=Pos)) + geom_boxplot()

bp7 <- ggplot(data,  aes(x=Pos, y=SoT., fill=Pos)) + geom_boxplot()
bp8 <- ggplot(data,  aes(x=Pos, y=PasTotCmp., fill=Pos)) + geom_boxplot()
bp9 <- ggplot(data,  aes(x=Pos, y=TklDri., fill=Pos)) + geom_boxplot()
bp10 <- ggplot(data,  aes(x=Pos, y=Press., fill=Pos)) + geom_boxplot()
bp11 <- ggplot(data,  aes(x=Pos, y=DriSucc., fill=Pos)) + geom_boxplot()
bp12 <- ggplot(data,  aes(x=Pos, y=Rec., fill=Pos)) + geom_boxplot()
bp13 <- ggplot(data,  aes(x=Pos, y=`AerWon%`, fill=Pos)) + geom_boxplot()


bp1
bp7
bp8
bp9
bp10
bp11
bp12
bp13
```


```{r}

data <- forwards %>% select(Nation, Goals_tot, PresSucc, GCA, Blocks, Err, Recov, SoT., PasTotCmp., TklDri.,Press., DriSucc., Rec., `AerWon%`)  

data_ <- data %>% group_by(Nation) %>% summarise(total_count=n())
data_ <- data_[order(-data_$total_count),] 
my_second_df <- filter(data,Nation %in% data_$Nation[1:10])
vp1 <- ggplot(my_second_df,  aes(x=Nation, y=Goals_tot, fill=Nation)) + geom_violin(width=1.4) + geom_boxplot(width=0.1, color="grey", alpha=0.2)
vp2 <- ggplot(my_second_df,  aes(x=Nation, y=PresSucc, fill=Nation)) + geom_violin(width=1.4) + geom_boxplot(width=0.1, color="grey", alpha=0.2)
vp3 <- ggplot(my_second_df,  aes(x=Nation, y=GCA, fill=Nation)) + geom_violin(width=1.4) + geom_boxplot(width=0.1, color="grey", alpha=0.2)
vp4 <- ggplot(my_second_df,  aes(x=Nation, y=Blocks, fill=Nation)) + geom_violin(width=1.4) + geom_boxplot(width=0.1, color="grey", alpha=0.2)
vp5 <- ggplot(my_second_df,  aes(x=Nation, y=Err, fill=Nation)) + geom_violin(width=1.4) + geom_boxplot(width=0.1, color="grey", alpha=0.2)


vp7 <- ggplot(my_second_df,  aes(x=Nation, y=SoT., fill=Nation)) + geom_violin(width=1.4) + geom_boxplot(width=0.1, color="grey", alpha=0.2)
vp8 <- ggplot(my_second_df,  aes(x=Nation, y=PasTotCmp., fill=Nation)) + geom_violin(width=1.4) + geom_boxplot(width=0.1, color="grey", alpha=0.2)
vp9 <- ggplot(my_second_df,  aes(x=Nation, y=TklDri., fill=Nation)) + geom_violin(width=1.4) + geom_boxplot(width=0.1, color="grey", alpha=0.2)
vp10 <- ggplot(my_second_df,  aes(x=Nation, y=Press., fill=Nation)) + geom_violin(width=1.4) + geom_boxplot(width=0.1, color="grey", alpha=0.2)
vp11 <- ggplot(my_second_df,  aes(x=Nation, y=DriSucc., fill=Nation)) + geom_violin(width=1.4) + geom_boxplot(width=0.1, color="grey", alpha=0.2)
vp12 <- ggplot(my_second_df,  aes(x=Nation, y=Rec., fill=Nation)) + geom_violin(width=1.4) + geom_boxplot(width=0.1, color="grey", alpha=0.2)
vp13 <- ggplot(my_second_df,  aes(x=Nation, y=`AerWon%`, fill=Nation)) + geom_violin(width=1.4) + geom_boxplot(width=0.1, color="grey", alpha=0.2)

vp1
vp2
vp3
vp4
vp5

vp7
vp8
vp9
vp10
vp11
vp12
vp13

```
```{r}
allPlayersCorr <- players %>% select(Goals_tot, PresSucc, GCA, Blocks, Err, Recov, SoT., PasTotCmp., TklDri.,Press., DriSucc., Rec., `AerWon%`)
forwardsCorr <- forwards %>% select(Goals_tot, PresSucc, GCA, Blocks, Err, Recov, SoT., PasTotCmp., TklDri.,Press., DriSucc., Rec., `AerWon%`)
defendersCorr <- defenders %>% select(Goals_tot, PresSucc, GCA, Blocks, Err, Recov, SoT., PasTotCmp., TklDri.,Press., DriSucc., Rec., `AerWon%`)
midfieldersCorr <- midfielders %>% select(Goals_tot, PresSucc, GCA, Blocks, Err, Recov, SoT., PasTotCmp., TklDri.,Press., DriSucc., Rec., `AerWon%`)
goalKeepersCorr <- goal_keepers %>% select(Goals_tot, PresSucc, GCA, Blocks, Err, Recov, SoT., PasTotCmp., TklDri.,Press., DriSucc., Rec., `AerWon%`)


ggcorr(allPlayersCorr, method = c("everything", "pearson")) 
ggcorr(forwardsCorr, method = c("everything", "pearson")) 
ggcorr(defendersCorr, method = c("everything", "pearson")) 
ggcorr(midfieldersCorr, method = c("everything", "pearson")) 
ggcorr(goalKeepersCorr, method = c("everything", "pearson")) 
```


```{r}
posNation <- players %>% select(Pos, Nation)

posNation$Pos[players$Pos == "DF" | players$Pos == "DFMF" | players$Pos == "DFFW"] <- "DF"
posNation$Pos[players$Pos == "MF" | players$Pos == "MFFW" | players$Pos == "MFDF"] <- "MF"
posNation$Pos[players$Pos == "FW" | players$Pos == "FWMF" | players$Pos == "FWDF"] <- "FW"
posNation$Pos[players$Pos == "GK" | players$Pos == "GKMF" ] <- "GK"

posByNation <- posNation %>% group_by(Nation) %>% summarise(total_count=n())
posByNation <- posByNation[order(-posByNation$total_count),] 
posByNation

ggplot(posNation, aes(fill=Nation, y=Nation %in% posByNation$Nation[1:10], x=Pos)) + geom_bar(position="dodge", stat="identity")

```

